Measuring contrast processing in the visual system using SSVEP (and VEP?)

### 2024-04-01 review.qmd
No message

# Contrast processing - gain control
Previous figures showed how a single-input SSVEP might generate a single peak in the FT response which, in turn, can be used as a read-out of neuronal activity.  Here, we show that adding a second contrast component can generate intermodulation and that the two components interact. The nature of the interaction is determined by the precise computations happening as the contrast signal moves from retina to cortex.

>>>>

# Contrast processing - gain control
Previous figures showed how a single-input SSVEP might generate a single set of peaks in the frequency domain response which, in turn, can be used as a read-out of neuronal activity.

Here, we show that adding a second contrast component can generate intermodulation and that the two components interact. The nature of the interaction is determined by the precise computations happening as the contrast signal moves from retina to cortex.
